\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}
\bibitem{ChapterTwo:Introduction to HTML and CSS}
\href{https://buildmedia.readthedocs.org/media/pdf/htmlguide/latest/htmlguide.pdf}{HTML Guide.}
\bibitem{ChapterTwo:Introduction to HTML and CSS} \href{https://www.austincc.edu/hr/profdev/eworkshops/docs/HTML_Basics.pdf}{HTML Basics.}
\bibitem{ChapterTwo:Introduction to HTML and CSS} \href{https://www.alvinisd.net/cms/lib03/TX01001897/Centricity/Domain/1077/beginning_html5_and_css3.pdf}{HTML5 and CSS3 Basics.}
\bibitem{ChapterTwo:Introduction to HTML and CSS}
\href{https://developer.mozilla.org/en-US/docs/Web/CSS/CSS3}{CSS3-Documentation}
\bibitem{ChapterThree:Introduction to Django} \href{https://buildmedia.readthedocs.org/media/pdf/django/latest/django.pdf}{Django documentation.}
\bibitem{ChapterThree:Introduction to Django } \href{https://docs.djangoproject.com/en/1.8/misc/design-philosophies/}{Django Design philosophies.}

\bibitem{ChapterFour:Introduction to Django Models} \href{https://buildmedia.readthedocs.org/media/pdf/django/latest/django.pdf}{Django documentation.}
\bibitem{ChapterFour:Introduction to Django Models}
\href{https://github.com/PacktPublishing/Django-Projects-Blueprints}{Django Project Blueprint.}
\bibitem{ChapterFive:Introduction to Django Forms}
\href{https://www.oreilly.com/library/view/django-project-blueprints/9781783985425/}{Django Project Blueprints.}

\bibitem{ChapterFive:Introduction to Django Forms}
\href{https://docs.djangoproject.com/en/2.2/topics/forms/}{Django Forms.}
\bibitem{Future Scope}
\href{https://simpleisbetterthancomplex.com/tutorial/2018/08/13/how-to-use-bootstrap-4-forms-with-django.html}{Bootstrap 4 Forms in Django.}
\bibitem{Future Scope}
\href{https://simpleisbetterthancomplex.com/tutorial/2018/08/13/how-to-use-bootstrap-4-forms-with-django.html}{Bootstrap 4 Forms in Django using crispy forms.}
\end{thebibliography}